Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-21 robdml.tex
abs
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% ICS
	\oo{ICS}
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method, albeit remains
	simple, overwhelmingly outperforms the state-of-the-art defense
	methods in terms of robustness, training cost, as well as recall
	performance on benign examples.
%
\end{abstract}

@@

@@

\begin{equation}
	%
	g_\mathsf{B}(H(\cdots)) = H(\cdots) + \xi \cdot \bar{\ell}_{t-1}
	%
\end{equation}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	Conversely, we argue that a model can learn from a strong adversary without
	collapse, where the key is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb the
	training triplet to increase its hardness into a specified level, by
	referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	Based on this, Gradual Adversary is proposed as a family of pseudo-hardness
	functions to overcome problems of referencing other benign triplets, and
	achieve a better balance in the learning objective.
	% Intra-Class Structure
	Besides, a penalty on Intra-Class Structure among benign and adversarial
	examples, which has been neglected by existing methods, can be used to
	further improve the model robustness.
	% Experiment and Conclusion
	Comprehensive experimental results on three commonly used deep metric
	learning datasets suggest that the proposed method, albeit remains
	simple, overwhelmingly outperforms the state-of-the-art defense
	methods in terms of robustness, training cost, as well as recall
	performance on benign examples.
%
\end{abstract}

@@

% motivation of GA : late phase

When benign triplets are used as reference for destination hardness, the
adversary (\ie, hardness of adversarial triplets) could gradually become weaker
than it should be in the late phase of training.
%
During the training process of a DML model, the expectation of the triplet loss
$E[L_\text{T}(\cdots)]$ on benign examples is gradually decreasing
(with the lower bound being zero).
%
The corresponding expectation of hardness $E[H(\cdots)]$ will
decrease as well (with the lower bound being $-\gamma$).
%
As a result, $E[H_\mathsf{D}-H_\mathsf{S}]$ will gradually tend to zero,
indicating a gradually decreasing strength of attack, and inefficiency in
learning from a strong adversary.

%

@@

\begin{equation}
	%
	g_\mathsf{B}(H(\cdots);\xi) = H(\cdots) + \xi \cdot (1-\bar{\ell}_{t-1})
	%
\end{equation}
